### 2022-01-06 input/proposal.tex
skeletton for xascast, discarded for submit

To further reduce the traffic generated by our DCP protocol, we
leverage that an Edge infrastructure is a network of autonomous
systems, only a small subset of which needs logical partitioning.

@@

@@

To enable LDCP in an Edge infrastructure, we use the property provided
by DCP in an autonomous system to all its \processes and among others,
to its gateways.

>>>>

\input{input/figxasproblem.tex}

To further reduce the traffic generated by our DCP protocol, we
leverage that an Edge infrastructure is a \TODO{network of autonomous
systems}, only a small subset of which needs logical partitioning.

@@

\begin{definition}[\TODO{Adjacent networks}]
\end{definition}

@@

\TODO{A naive implementation would consist in using gateways as
  additional gatekeepers of scoped broadcast. Figure that shows that
  it works mostly.}

\begin{lemma}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{G} \centernot\implies \textup{LDCP}$]
  \TODO{meow}
\end{lemma}

\begin{proof}
  \TODO{meow meow}
\end{proof}

\TODO{To enable LDCP in an Edge infrastructure, we use the property provided
by DCP in an autonomous system to all its \processes and among others,
to its gateways.}
